Verifying Demonstrations

### 2018-11-12 paper/intro.tex
coincoin

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating (\ie their claims should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.

@@

In this paper, our first main contribution is to propose \PRIVO, a 
privacy-preserving scheme providing a way to securely estimate crowd count in 
protests.
%\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
%Seb: I am ok with the change done

@@

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, the protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times ---, which in turn increases the error of the estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claims should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
%Seb: in the sentence above I am not sure that the word unlinkable will be necessary clear

@@

In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

@@

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

### 2018-11-12 paper/privacy-properties.tex
coincoin

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how a elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

@@

\daniel{%
  In our case:
  I have a key issued on a smartcard and it's tied to my identity.
  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
    \ACprf[_k][\cid']\).
  I could've downloaded both from the ledger.
  But I know which is mine, I can submit it, and as long as the block where it 
  was included is intact I know my proof-share is included as well --- even if 
  I forget what it looked like.%
}

@@

\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, is a slight increase in privacy over ordinary protests.}

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how a elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

@@

\daniel{%
  In our case:
  I have a key issued on a smartcard and it is tied to my identity.
  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
    \ACprf[_k][\cid']\).
  I could have downloaded both from the ledger.
  But I know which is mine, I can submit it, and as long as the block where it 
  was included is intact I know my proof-share is included as well --- even if 
  I forget what it looked like.%
}

@@

%Seb: ok for me, I have put it in comment
%\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
%This is, in fact, is a slight increase in privacy over ordinary protests.}

### 2018-11-12 paper/timestamp.tex
coincoin

With these building blocks we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), a user submits \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

@@

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain (the head).
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus where the computing power of the honest participants must outpower the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin where blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her proof and the hash of the proof. \sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}

>>>>

With these building blocks, we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), a user submits \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

@@

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her participation proof and the hash of the proof.

### 2018-11-12 paper/verifiability-properties.tex
coincoin

We draw inspiration from the three traditionally desired properties for 
verifiability for voting:
% XXX find a new ref for voting verifiability properties
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    % Douglas: technically this is Sako-Kilian
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    % Douglas: this is much earlier than Sako-Kilian, in essence Fiat-Shamir.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also has some temporal aspects, \eg one cannot vote at any time and 
  a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as 
  for elections, a protest can start at any time and last for an arbitrary 
  period of time.
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To adapt these properties to the context of protests, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
    \end{requirements}

>>>>

We draw inspiration from the three traditionally desired properties for verifiability for voting:
% XXX find a new ref for voting verifiability properties
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    % Douglas: technically this is Sako-Kilian
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    % Douglas: this is much earlier than Sako-Kilian, in essence Fiat-Shamir.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must include temporal\footnote{
Elections also have some temporal aspects, such that one cannot vote at any time and a vote in one election should not be reusable in the next election.
However, the temporal relation for a protest is not as strictly defined as for elections as a protest can start at any time and last for an arbitrary period of time.}
%Seb: the starting and ending time of the protest could also be included in the manisfest if we wanted to 
and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To adapt these properties to the context of protests, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    %Seb: this property seems to be related to the eligibility property in the sense that if a participant tries to submit a second proof this directly conflicts with the eligibility
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
    \end{requirements}
